Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-10-10 paper.tex
Remove erroneous comment
Text wrapping

Blackwell et al. investigated the effects of Reynolds number on the
performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed high Reynolds
number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$.
\todo[inline]{Add reference for Bravo et al.}
\todo[inline]{Why did you take Polagye and Cavagnaro citation out - not
relevant?}
\todo[inline]{bring back the examples of studies at small scale? (too small)}

@@

From each set of tows, a standard time interval was set, which allowed the
turbine performance and wake to reach a quasi-periodic state. Each run was
analyzed to compute statistics over this interval, truncating the end slightly
to achieve and integer number of blade passages. Turbine shaft angular velocity
and tow carriage speed were calculated using a second order central differencing
scheme on the respective position measurements. Power and drag coefficients are
calculated as instantaneous quantities using the carriage speed as the free
stream velocity.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/perf_re_dep}
\caption{UNH-RVAT measured mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.}
\label{fig:perf-Re-dep}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.85\textwidth]{figures/wake_spectra}
\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$,
$y/R=-1.0$ ($-0.5$ m in Figure~\ref{fig:wake-locations}) (a) and $y/R=1.5$ ($+0.75$ m in Figure~\ref{fig:wake-locations}) (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}

>>>>

Blackwell et al. investigated the effects of Reynolds number on the
performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed high Reynolds
number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$.
\todo[inline]{Add reference for Bravo et al.}

\todo[inline]{bring back the examples of studies at small scale? (too small)}

@@

From each set of tows, a standard time interval was set, which allowed the
turbine performance and wake to reach a quasi-periodic state. Each run was
analyzed to compute statistics over this interval, truncating the end slightly
to achieve and integer number of blade passages. Turbine shaft angular velocity
and tow carriage speed were calculated using as second order central
differencing scheme on the respective position measurements. Power and drag
coefficients are calculated as instantaneous quantities using the carriage speed
as the free stream velocity.

@@

\begin{figure}[ht]
\centering

\includegraphics[width=0.9\textwidth]{figures/perf_re_dep}

\caption{UNH-RVAT measured mean power (left) and drag (right) coefficients at
    $\lambda=1.9$ plotted versus Reynolds number.}

\label{fig:perf-Re-dep}
\end{figure}

@@

\begin{figure}[ht!]
\centering

\includegraphics[width=0.85\textwidth]{figures/wake_spectra}

\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$,
    $y/R=-1.0$ ($-0.5$ m in Figure~\ref{fig:wake-locations}) (a) and $y/R=1.5$
    ($+0.75$ m in Figure~\ref{fig:wake-locations}) (b). Dashed vertical lines
    indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}

\label{fig:wake-spectra}
\end{figure}
